\section{Methods to reduce jams}
A technology to increase safety for drivers in traffic is Adaptive Cruise Control (ACC) which is the next generation of cruise control. This kind of system is able to measure the distance and speed to the car infront and then adapt the speed so a certain time gap is maintained between the cars. ACC is already commercially available on the market and there is much research going on to see the effect in traffic flow when more and more vehicles are equipped with this system \cite{acc}. The biggest advantage of the system is the increased comfort of the driver but also safety is increased. A human driver is mostly not good at estimating the distance or the velocity to the car in front which can cause unneccessary brakes or accelerations in the traffic flow. Also because of some drivers behaviour the time headway between the cars is even shorter than the reaction time of a normal driver which reduces the ability of a driver to adapt to changes of traffic flow. Since ACC is able to measure the distance and velocity with good precision and adapts the speed to always keep a safe time headway to the car in front there isn't neccessary to do as much braking and acceleration. (FIXME: ref till not)

One ability that human drivers have but not ACC is the possibility to look ahead in traffic. One example is the braking light that can be seen through several cars and this ability increses both safety and in some cases traffic flow. A problem with this method is the difficulty to estimate the speed of the cars ahead. The only information available is that the cars further ahead are breaking. We have thought of system that have the advantages of the ACC and the possibility to look further ahead in traffic. This enhanced model could be realized by communication between the cars that are travelling in the same direction. There has been some research on communication between cars and (FIXME: Kesting et al. ) have tested the connectivity of such a system. The enhanced system can then adapt the speed to the cars further up in line depending of position and velocity and then possibly reduce stop \& go-traffic.